DOM Review Summary

### 2024-03-18 Analysis/ReviewSummary/ReviewSummary.qmd
Covariate quantity
Cleaned covariate data; added plots for number of covariates

The most common objective was **Testing Hypotheses**, with `{r} max(objectives_frequency$Proportion)`% of articles examining pre-determined relationships. Prediction, whether spatial or temporal, was rare.

@@

```{r Species_clean}
species_clean <- review_SpeciesLocation |>
  filter(Status == "Complete") |>
  mutate(ID_clean = str_extract(ID, "[:digit:]+"))
```

@@

@@

>>>>

The most common objective was **Testing Hypotheses**, with `{r} round(max(objectives_frequency$Proportion), 2)`% of articles examining pre-determined relationships. Prediction, whether spatial or temporal, was rare.

@@

```{r Species_clean}
#| echo: false
species_clean <- review_SpeciesLocation |>
  filter(Status == "Complete") |>
  mutate(ID_clean = str_extract(ID, "[:digit:]+"))
```

@@

```{r Covariates_clean}
#| echo: false

covariates_clean <- review_Covariates |>
  filter(Status == "Complete") |>
  mutate(ID_clean = str_extract(ID, "[:digit:]+")) |>
  mutate(Covariates = str_replace(Covariates, "\\.", "\\,")) |>
  separate_rows(Covariates, sep = ", ") |>
  mutate(Covariates = str_to_upper(Covariates)) |>
  separate_wider_delim(cols = Covariates, delim = "_",
                       names = c("Type", 
                                 "Variation",
                                 "Measurement",
                                 "Complexity"),
                       too_few = "align_start", 
                       too_many = "drop") |>
  mutate(ParameterCategory = case_when(Parameter %in% c("InitialOccupancy",
                                                        "InitialOccupancy_MS",
                                                        "Occupancy",
                                                        "Occupancy_MS") ~ "Psi",
                                       Parameter %in% c("Colonisation",
                                                        "Colonisation_MS") ~ "Gamma",
                                       Parameter %in% c("Extinction",
                                                        "Extinction_MS",
                                                        "Persistence",
                                                        "Persistence_MS") ~ "Eps",
                                       Parameter %in% c("Detection",
                                                        "Detection_FP",
                                                        "Detection_FP_MS",
                                                        "Detection_MS", 
                                                        "Detection_Other") ~ "p",
                                       .default = "Other"),
         Type = case_when(Type %in% c("E-HTT", " E-HTT") ~ "E-HTT",
                          Type %in% c("E-DIS", "DIS") ~ "E-DIS",
                          Type %in% c("ANTH", "E-ANTH") ~ "E-ANTH",
                          Type %in% c("SP", "Spec") ~ "SP",
                          Type %in% c("NONE", "NA") ~ "NONE",
                          .default = Type),
         Variation = case_when(Variation %in% c("SY", "YS") ~ "Site-Year",
                               Variation == "S" ~ "Site",
                               Variation == "YSS" ~ "Site-Year-Survey",
                               Variation == "Y" ~ "Year",
                               Variation == "SP" ~ "Species",
                               Variation == "U" ~ "Unclear"),
         Measurement = case_when(Measurement == "I" ~ "Intrinsic",
                                 Measurement == "O" ~ "Observed",
                                 Measurement == "R" ~ "Remote",
                                 Measurement == "U" ~ "Unclear"),
         Complexity = case_when(Complexity %in% c("N", "NH", "N,") ~ "Linear",
                                Complexity == "Q" ~ "Quadratic",
                                Complexity == "I" ~ "Interaction",
                                Complexity == "B" ~ "Quadratic + Interaction",
                                Complexity == "O" ~ "Other"))
```

@@

::: panel-tabset
## Overall

```{r covariates_quantityOverall}
#| echo: false

covariates_clean |>
  filter(Type != "NONE") |>
  summarise(Covariates = n(), .by = ID) |>

  ggplot() +
  geom_histogram(aes(x = Covariates), 
                 binwidth = 5,
                 fill = "darkslategrey") +
  labs(title = "Total number of covariates considered",
       subtitle = "All parameters",
       x = "Number of covariates", y = "Number of articles")
```

## By parameter

```{r covariates_quantityParameter}
#| echo: false

covariates_clean |>
  filter(Type != "NONE") |>
  summarise(Covariates = n(), .by = c(ID, ParameterCategory)) |>
  filter(ParameterCategory != "Other") |>
  mutate(ParameterCategory = case_when(ParameterCategory == "Psi" ~ "Initial Occupancy",
                                       ParameterCategory == "Gamma" ~ "Colonisation",
                                       ParameterCategory == "Eps" ~ "Extinction",
                                       ParameterCategory == "p" ~ "Detection")) |>
  complete(ID, ParameterCategory, fill= list(Covariates = 0)) |>
  mutate(ParameterCategory = fct(ParameterCategory,
                                 levels = c("Initial Occupancy",
                                            "Colonisation", 
                                            "Extinction",
                                            "Detection"))) |>
  mutate(Covariates = case_when(Covariates > 10 ~ 10,
                                .default = Covariates)) |>

  ggplot() +
  geom_histogram(aes(x = Covariates, fill = ParameterCategory), 
                 binwidth = 1) +
  labs(title = "Total number of covariates considered",
       x = "Number of covariates", y = "Number of articles") +
  scale_fill_manual(values = c("darkslategrey", "darkorchid", 
                               "cyan2", "goldenrod")) +
  scale_x_continuous(breaks = c(0, 5, 10), 
                     labels = c("0", "5", "10+")) +
  facet_grid(rows = vars(ParameterCategory)) +
  theme(legend.position = "none")
```
:::
